
```{r}
#| echo: false
#| message: false
googledrive::drive_auth(email = Sys.getenv("GMAIL_ROG"))

if (!dir.exists('csv')) {
  dir.create('csv')
}

csv_fn <- "csv/sched.csv"

googledrive::drive_download(
  file = 'PSY-548.001-2025-Fall',
  path = csv_fn,
  type = 'csv',
  overwrite = TRUE
)

if (file.exists(csv_fn)) {
  sched_df <- readr::read_csv(csv_fn, show_col_types = FALSE)
} else {
  message("File not found: ", csv_fn)
  sched_df <- NULL
}

sched_df <- sched_df |>
  dplyr::mutate(class_day = lubridate::as_date(class_date))
```

```{r}
#| label: helper-functions
#| echo: false
#| message: false

prettify_date <- function(date) {
  paste0(
    lubridate::wday(date, label = TRUE), ", ",
    lubridate::month(date, label = TRUE),
    " ",
    lubridate::day(date),
    ", ",
    lubridate::year(date)
  )
}
```


## `{r} sched_df$week[1]` {- #week-01}

### `{r} prettify_date(sched_df$class_day[1])` {-}

#### Topics

- What is cognition?
- Why study cognitive development?

#### Readings

- SA: Ch 1
- @Bayne2019-ot

## `{r} sched_df$week[2]` {- #week-02}

### `{r} prettify_date(sched_df$class_day[2])` {-}

#### Topics

- Theoretical foundations: Information processing

#### Readings

- SA: Ch 3
- @Simmering2010-ba

## `{r} sched_df$week[3]` {- #week-03}

### `{r} prettify_date(sched_df$class_day[3])` {-}

#### Topics

- Theoretical foundations: Piaget

#### Readings

- SA: Ch 2

## `{r} sched_df$week[4]` {- #week-04}

### `{r} prettify_date(sched_df$class_day[4])` {-}

#### Topics

- Theoretical foundations: Sociocultural development

#### Readings

- SA: Ch 4

## `{r} sched_df$week[5]` {- #week-05}

### `{r} prettify_date(sched_df$class_day[5])` {-}

#### Topics

- Perceptual development: Overview

#### Readings

- SA: Ch 5

## `{r} sched_df$week[6]` {- #week-06}

### `{r} prettify_date(sched_df$class_day[6])` {-}

#### Topics

- Perceptual development: Deep dive

#### Readings

- @Haith1998-vu

## `{r} sched_df$week[7]` {- #week-07}

### `{r} prettify_date(sched_df$class_day[7])` {-}

#### Topics

- Motor development

#### Readings

- @Adolph1042-oj, @Blumberg2023-ce

## `{r} sched_df$week[8]` {- #week-08}

### `{r} prettify_date(sched_df$class_day[8])` {-}

#### Topics

- Language development

#### Readings

- SA: Ch 6

## `{r} sched_df$week[9]` {- #week-09}

### `{r} prettify_date(sched_df$class_day[9])` {-}

#### Topics

- Language development: Deep dive

#### Readings

- @Chomsky1959-ef

## `{r} sched_df$week[10]` {- #week-10}

### `{r} prettify_date(sched_df$class_day[10])` {-}

#### Topics

- Memory development: Overview

#### Readings

- SA: Ch 7

## `{r} sched_df$week[11]` {- #week-11}

### `{r} prettify_date(sched_df$class_day[11])` {-}

#### Topics

- Memory development: Deep dive

#### Readings

- TBD

## `{r} sched_df$week[12]` {- #week-12}

### `{r} prettify_date(sched_df$class_day[12])` {-}

#### Topics

- Conceptual development: Overview

#### Readings

- SA: Ch 8

## `{r} sched_df$week[13]` {- #week-13}

### `{r} prettify_date(sched_df$class_day[13])` {-}

#### Topics

- Conceptual development: Deep dive

#### Readings

- TBD

## `{r} sched_df$week[14]` {- #week-14}

**NO CLASS**

## `{r} sched_df$week[15]` {- #week-15}

### `{r} prettify_date(sched_df$class_day[15])` {-}

#### Topics

- Social cognition

#### Readings

- SA: Ch 9

## `{r} sched_df$week[16]` {- #week-16}

### `{r} prettify_date(sched_df$class_day[16])` {-}

#### Topics

- Problem solving

#### Readings

- TBD
